Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-14 presentations/bsa_2020-07-27/index.Rmd
Change citation style

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(
  ignore.case = TRUE,
  check.entries = FALSE, 
  style = "markdown"
)
bib <- ReadBib(here::here("presentations/bsa_2020-07-27/refs.bib"), check = FALSE)
```

>>>>

```{r, load_refs, includ = FALSE, cache = FALSE}
# Set bibliography options
library(RefManageR)
BibOptions(
  ignore.case = TRUE,
  check.entries = FALSE, 
  bib.style = "authoryear", # set style of bibliography as e.g., "Nitta 2020..."
  style = "text" # set style of citations as plain text (no links)
)

# Read in bibliography
bib <- ReadBib(here::here("presentations/bsa_2020-07-27/refs.bib"), check = FALSE)
```
